\bf A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes

### 2017-10-04 paper/paper.tex
More edits to bibtek and paper.  focused on results section.

The reliability of many engineered products follow a similar pattern. Relatively high rates of failure occurring early (``infant mortality'') due to manufacturing defects.  After this ``burn-in'' period, failure rates stabilize as the majority of defective units have failed and are no longer in the population.  Finally, after prolonged use, rates of failure increase due to wearout.  Ignoring this pattern in failure rates can lead to suboptimal decisions and spurious inferences about a product's reliability. This highlights the importance of choosing a sufficiently flexible model.

Nonparametric methods require relatively few assumptions, but they are not suitable for forecasting. Moreover, nonparametric estimates made using small samples, or data which are heavily censored may be too noisy to be practical. Appropriate parametric models can make better use of available data. For inference, likelihood-based methods are well-equipped to deal with truncated and/or censored data. Furthermore, by assuming a parsimonious representation of the data-generating process, parametric models admit simpler, more intuitive ways to compare populations of interest, borrow strength across groups, and incorporate prior information.

Often no information is available to identify why a unit failed and even when the failed units are available, physical failure mode analysis (sometimes referred to as ``autopsy'') can be extremely time consuming and expensive. This presents a dilemma for analysts: the data may indicate multiple failure modes, contraindicating the use of a unimodal parametric distribution. However, without any knowledge of cause of failure, traditional competing risk models are not identifiable. \citet{chan} proposed the Generalized Limited Failure Population (GLFP) model. This model can provide a solution to the problem of unknown cause of failure (masking) in the special case where there is evidence of two modes of failure which impact different stages of product life. It avoids non-identifiability by introducing a parameter representing the population proportion defective. Where this parameter is zero, the GLFP model reduces to a unimodal distribution. \\

@@

The structure of the paper is as follows. Section~\ref{sec:Background} introduces the proposed method and potential applications and examines previous related work in the literature.  Section~\ref{sec:GLFP model} introduces the GLFP model and illustrates its use with a subset of the Backblaze data.  In Section~\ref{sec:Data}, we describe the Backblaze Hard Drive data set, which is used throughout as a motivating example. In section~\ref{sec:Hierarchical GLFP model} we discuss using hierarchical modeling of the GLFP model parameters to extend the GLFP model to multiple populations. Section~\ref{sec:Data analysis} applies the hierarchical GLFP model to the hard disk drive data. First, we do model selection among four models of increasing complexity, using approximate leave-one-out cross-validation. Next, for the selected model, we assess the model fit using a graphical comparison of replicated data sets generated from the posterior distribution to the observed data. Finally, we present an evaluative comparison of populations taking into account practical considerations related to product lifetime. Finally, in section~\ref{sec:Discussion}, we suggest potential applications of our model and consider limitation for inference implied by the model assumptions.

@@

Previous papers have employed various data assumptions and methodologies to model masked lifetime failure data.  When modeling computer system failures \citet{reiser} assumed each observed failure came from a known subset of failure modes, and estimation was performed using a Bayesian approach.  \cite{chan} labeled the cause of circuit board failures as infant mortality, unknown, or wearout based on the time of observed failures.  This helped identify parameters when using maximum likelihood (ML) estimation.  Extending Chan and Meeker's analysis, \citet{basu} performed a Bayesian analysis with informative priors to better identify early versus late failure modes without making any assumptions about the cause of failure.  \cite{berger} introduced the Poly-Weibull distribution where cause of failure is the minimum of a several Weibull distributions.  More recently, \cite{ranjan} considered a competing risk model for infant mortality and wearout as a mixture of Weibull and exponential failure distributions.  Treating the unknown failure modes as incomplete data, an expectation maximization (EM) algorithm providing ML estimates was used, in addition to Bayesian estimation.

@@

In order to describe the entire population, consisting of different but similar sub-populations, and because of the limited amount of data from many of the sub-populations, we model the sub-population specific parameters hierarchically, borrowing strength across the sub-populations.  Let
\begin{equation}
y_{ig} \ind \op{GLFP}\left( \pi_g, \mu_{1g}, \sigma_{1g}, \mu_{2g}, \sigma_{2g} \right),
\end{equation}
where $g=1,\ldots,G$ indexes the sub-populations.  The likelihood for the hierarchical GLFP is a function of $\bm{\theta_g} = (\mu_{1g}, \sigma_{1g}, \mu_{2g}, \sigma_{2g}, \pi_{g})$.  Assuming the lifetimes of all units are independent within and across groups, the likelihood for the data, $i=1,\dots,n_g$,  is given by
\begin{equation*}
L(\bm{\Theta})= \prod_{g=1}^{G} \prod_{i=1}^{n_{g}} \left[\frac{f(t_{ig};\bm{\theta_g})}{1-F(t_{ig}^L;\bm{\theta_g})}\right]^{1-c_{ig}} \left[ \frac{1-F(t_{ig};\bm{\theta_g})}{1-F(t_{ig}^L;\bm{\theta_g})} \right]^{c_{ig}}
\end{equation*}
where $t_{ig}$ is the end of the observed lifetime of unit $i$ in group $g$; $t_{ig}^L$ is the left truncation time for unit $i$ in group $g$; and $c_{ig}$ is an indicator if unit $i$ in group $g$ is right censored.  All times are again in hours.

@@

As discussed in Section \ref{sec:Weibull parameterization}, we reparameterize the Weibull distribution in terms of log quantile and scale since the data we encounter are more informative about the left side of their respective lifetime distribution. We truncate the distribution of $\sigma_{2g}$ at $1$, restricting the wearout failure mode to have an increasing hazard function. We choose to model these parameters (or suitable transformations) with normal distributions because many populations require strong regularization which the normal, with its exponentially decreasing tails, provides.

@@

The set of model specifications were chosen based data, interpretation of the model, as well as estimation considerations.  Product specific parameters for the the wearout failure mode $(\mu_{2g},\sigma_{2g})$, and the proportion defective $(\pi_g)$, are considered as a means to account for heterogeneity across brands in the right tails of the failure distribution.  Going from a common model for all product brands and gradually increasing the complexity of the model, we end up at Model 4.  Model 4 allows for the probability of infant mortality as well as the shape and scale parameters for the wearout failure mode to vary by Drive-model.

@@

\paragraph{Model 2.} $t_{p,g}$ varies by Drive-model. To help with model identifiably, we tighten the priors on the infant mortality failure mode:
$$ \pi \sim \op{Logit-normal}\langle 7.0\times 10^{-3},\, 2.6 \times 10^{-1} \rangle,$$
$$\sigma_1 \sim \op{Log-normal}\langle 1.4 \times 10^{-1},\, 7.1\rangle,$$ 
$$t_{p1} \sim \op{Log-normal} \langle 2.2 \times 10^1,\, 5.5 \times 10^{4} \rangle.$$

@@

\subsection{Model Selection}
\label{sec:Model Comparisons}
As we have discussed, while we prefer to allow all of the GLFP model parameters to be Drive-model specific, there are practical issues with fitting the full model. For example, due to heavy left-truncation, there may be insufficient information for particular drive-models to estimate all of the parameters.

Figure \ref{fig:fig2} provides a visual comparison for Models 1 through 4 by plotting the pointwise posterior median of time to failure. The large left panel shows the Kaplan-Meier nonparametric estimate of the same. The Kaplan-Meier estimates on the right side of Figure \ref{fig:fig2} shows that the set of estimated failure curves for all four models that we fit. The smaller plots correspond to Models 1 through 4 reading from left to right, top to bottom. Note that while all the paths for the posterior estimates necessarily pass through the origin, the nonparametric curves do not, but only because, for the Kaplan-Meier estimator, inference is entirely conditional on survival up to left-most left-trunctation time; to make the plot comparable, we use an adjustment based on a parametric model (Model 4).

%Should we be brief discussing the plot?
These plots suggest that Model 1 is insufficient to explain the observed data. Model 2 certainly captures more of the heterogeneity observed in the Kaplan-Meier estimates; we observe that the assumption of a common $\sigma_2(=\sigma_{2,g})$ results in a very similar progressions in the rate of failure, which may be too restrictive. Model 3, which removes this restriction on $\sigma_{2,g}$ suggests that there is evidence to support variation in this parameter among drive-models. While Model 3 and 4 do display differences, their impact is relatively subtle.

@@

We can also compare the four Model fits for each Drive-model individually.  For these comparisons, we use the posterior median of the MCMC draws. %Unlike maximum likelihood, by including the hyperparameters in the probability model, there is a data-dependent penalization that results in shrinkage toward a common overall model.

@@

The GLFP fit for a representative selection of drive-models (Drive-models 2, 9, 14, and 40) are presented in Figure \ref{fig:mod_comp_leg} (See the Supplementary Material for all plots).  The black step functions again correspond to the adjusted Kaplan-Meier estimates.  As model complexity increases, the GLFP curves become more flexible and are better able to fit the observed failure data.  All of the GLFP models appear to produce lower estimates, relative to Kaplan-Meier, of the proportion of failed hard drives for Drive-model 2, with Model 4 being in closest agreement.  For Drive-model 14, Models 1-3 produce lower estimates of the proportion of drives failing, and for Drive-model 40, they produce higher estimates.  On the other hand, Model 4 follows the nonparametric estimate quite closely across stages of lifetime.  The differences between Models 3 and 4 and Models 1 and 2 are visually quite apparent.  Differentiating between Model 3 and 4 is less clear; for instance, the estimates from Model 3 and 4 are nearly identical for Drive-model 40.

From the point of view of a consumer of hard disk drives, the goal of an analysis such as this is may be to rate manufacturers and/or to inform future purchases based on predicted product performance. In this case, we should choose the model that will provide the most accurate prediction for future units of previously observed drive-models. One appropriate criterion for model selection, then, is log pointwise predictive density (lpd),

@@

Using this criterion, we should choose the Model with the highest expected lpd (elpd) for a new data set $\{t_{new,g,i}:g=1,\ldots,G; i=1,\ldots,n_g\}$. Suppressing the conditioning on $t^L$ and $c$,
\begin{equation}
\mbox{elpd} = \op{E}_h \mbox{lpd} = \sum_{g=1}^G \sum_{i=1}^{n_g} \int \log [p(t_{new, g, i}|t)] h(t_{new,g,i}) d t_{new,g,i},
\label{elpd}
\end{equation}
where $h$ is a density for the true distribution of $t_{new,g,i}$. Although $h$ is unknown, leave-one-out cross-validation provides a robust estimator:
\begin{equation}
\widehat{\text{elpd}} = \sum_{g=1}^G \sum_{i=1}^{n_g} \log [p(t_{g,i}|t_{-(g,i)})].
\label{loo-est}
\end{equation}
The \texttt{R} package, \texttt{loo} \citep{loo}, computes an approximation of (\ref{loo-est}) provided that the observations $t_i$ are conditionally independent. It employs an importance sampling method that uses $S$ saved MCMC draws to compute smoothed importance weights, $w_{i,s}$, approximating $\log [p(t_{g,i}|t_{-(g,i)})]$ with $\frac{\sum_{i=1}^S w_{i,s} p(t_{g,i})}{\sum_{s=1}^S w_{i,s}}$. In addition to providing an estimate of (\ref{elpd}), their method also produces a standard error based on an asymptotic result. For details, refer to \cite{vehtari}.
%When $n$ is large, the distribution of the elpd is approximately normal and different models can be compared statistically. 
% To statistically compare the GLFP Models, we estimated the predictive accuracy of the 4 different models using an approximate leave-one-out cross validation (LOO) method.  As outlined in Vehtari et. al, the predictive accuracy from a fitted Bayesian model can be estimated simply with posterior draws of the model parameters rather than re-fitting the model with different data sets \cite{vehtari}.  For each observation, $i$, the log point-wise predictive density is calculated over the full set of posterior samples with data point $i$ removed.  
% The final expected log point-wise predictive density (elpd) is the sum over all observations (elpd $=\sum{\log p(y_i|y_{-i})}$).  
Results showing estimated elpd and associated standard errors for all 4 models are shown in Table \ref{table:2}.
 We calculated the difference in expected predictive accuracy for Model 4 versus 3, Model 3 versus 2, and Model 2 versus 1, as well as the standard error of the difference (Table 1).  
For the models we considered, each successive increase in model complexity increases elpd.  Of all the models, Model 4 has significantly better elpd compared to the the other 3 models.
\begin{figure}
\begin{table}[H]
\centering
\begin{tabular}{rrrrrrr}
  \hline
 & $\widehat{\text{elpd}}$ \ & Difference in $\widehat{\text{elpd}}$ \ & SE of the Difference \\ 
  \hline
Model 4 & -13309.5 & 40.7 & 11.3 \\ 
Model 3 & -13350.2 & 458.8 & 31.0  \\ 
Model 2 & -13809.0 & 3674.6 & 96.2 \\ 
Model 1 & -17483.6  \\ 
   \hline
\end{tabular}
\caption{Expected Log Pointwise Predictive Density (elpd) for each model specification.  Each model is compared to the more parsimonious model below.  The estimated difference of expected leave-one-out prediction errors between the two models, as well as the standard error of the difference, is also presented.}
\label{table:2}
\end{table}
\end{figure}
\subsection{Results}
\subsubsection{Model Assessment}
\label{model-assessment}
Having chosen Model 4 as the best of the candidate models, we would like to assess whether our model provides an adequate fit to the observed data. One way to do this is to draw replicate data sets from the posterior predictive distribution. This is a general approach recommended by \cite{gelman1996postpred} for models where no classical goodness-of-fit test is available. In the hierarchical setting, there can be different formulations of the predictive distribution. In the present context, one could predict the lifetime of a new unit of a previously observed Drive-model or a new Drive-model. We choose to focus on the former.  There are many possible approaches to the posterior predictive check. For this problem, we chose to consider the posterior predictive distribution of the Kaplan-Meier estimate for each Drive-model $g$.

@@

An obstacle remains, in that the censoring mechanism itself is not fully observed. Our admittedly simple approach is to assume that failed units would have been the censored had they survived until the latest censoring or failure time for that drive model. We chose to generate 19 replicates for each drive model. This gives a 1/20 chance under the hypothesis of no difference that the Kaplan-Meier estimate based on the observed data would be ``most extreme" relative all the replicated  from the those one and is not too many so as to produce an overly cluttered plot. Our method for generating replicate data sets, $y_{rep,g}^{(s)}$, $s = 1 \dots 19$, for each Drive-model $g=1,\ldots,44$, is as follows:
\begin{enumerate}
\item Simulate $\tilde{t}_{rep,g,i}^{(s)} \sim \op{GLFP}(\pi_{g}^{(s)},\mu_1^{(s)},\sigma_1^{(s)},\mu_{2g}^{(s)}, \sigma_{2g}^{(s)})$ where each set of parameters, $\left( \pi_{g}^{(s)},\mu_1^{(s)},\sigma_1^{(s)},\mu_{2g}^{(s)}, \sigma_{2g}^{(s)} \right) $, is a random draw from the full posterior distribution.
\item Repeat step 1 until $\tilde{t}_{rep,g,i} > t_{g,i}^L$.
\item If $c_{g,i}=0$, let $c_{rep,g,i}^{(s)}=\max \{t_{g,i}: i \ge 1\}$, otherwise let $c_{rep,g,i}^{(s)}=t_{g,i}$.\\
If $\tilde{t}_{rep,g,i}^{(s)}>m_{g,i}$, set $t_{rep,g,i}^{(s)}=c_{rep,g,i}^{(s)},\; c_{rep,g,i}^{(s)}=1$, otherwise set $t_{rep,g,i}^{(s)}=\tilde{t}_{rep,g,i}^{(s)},\; c_{rep,g,i}^{(s)}=0$.
\end{enumerate}

\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-sample}
\caption{Nonparametric estimates of proportion failing for a representative subset of drive-models. Both the original data (\textbf{bold} line) and 19 ``replicated" data sets from the posterior predictive distribution (\textit{dashed} lines) are shown.}
\label{fig:post-pred-KM}
\end{figure}

We can compare the 19 simulated data sets $y_{rep,g, i}$ to the observed data $y_{g,i}$ by using them to re-estimate the Kaplan-Meier nonparametric estimator. The resulting plots are displayed in Figure \ref{fig:post-pred-KM}. Only a representative sample of plots are shown here for brevity (see the Supplementary Material for the complete set of drive-models).  For most drive-models, the estimates based on the observed data look similar to those based on the replicated data.  There are a few drive-models, however where this is not the case. Drive-model 14 shows a discrepancy between the GFLP fit and the Kaplan-Meier fit in the right tail. In particular, the GLFP predictions appear conservative, overpredicting the proportion failing after about 2.5 years. Due to the large number of failures for this Drive-model, the posterior for the hierarchical model is very similar to the stand-alone model. Other drive-models showing a lack of fit are 4 and 34. We first address Drive-model 4; our diagnosis of 34 is analogous, so the following comments extend to that Drive-model as well.

@@

We can also use the posterior draws to compute quantiles of interest, which in reliability applications is typically more informative than a measure of central tendency.  The left panel of Figure 5 shows $t_{0.10}$ (i.e., the amount of time it takes for 10\% of hard drives to fail), for all drive-models. The best six drive-models ranked by MTTF are also the drive-models with the largest $t_{0.10}$.  Drive-models 5, 2, 4, and 3 seem to really stand out as the most reliable as there is a larger gap separating them from the rest of the group.  Another interesting feature to compare is $\pi$, the proportion defective.  The right panel of Figure 5 shows the posterior credible intervals of $\pi$ for each Drive-model.  The plot is again sorted according to $t_{0.10}$ so it can be compared to the left hand side.  While for many of the drive-models the ordinal ranking is the same as on the left, there are some Drive-model comparisons, for example 23 and 18, that differ in ranking if compared using $t_{0.10}$ or $\pi$.  Depending on a user's application or the hard drive warranty length, using the $\pi$'s as a comparison tool may be a relevant parameter of interest.

>>>>

The reliability of many engineered products follow a similar pattern. Relatively high rates of failure occurring early (``infant mortality'') due to manufacturing defects.  After this ``burn-in'' period, failure rates stabilize as the majority of defective units have failed and are no longer in the population.  Finally, after prolonged use, rates of failure increase due to wearout.  Ignoring this pattern in failure rates can lead to spurious inferences about a product's reliability and suboptimal decisions. This highlights the importance of choosing a sufficiently flexible model.

This paper presents a general framework for statistically modeling reliability field data from a heterogeneous population of components or subsystems operating within a larger population or fleet of systems. Such a model would be useful for applications such as making purchase decisions from among different suppliers of the components or subsystems.  Another application is making predictions for the number of needed replacement components or subsystems for spare part provisioning.

Nonparametric methods require relatively few assumptions, but they are not suitable for prediction. Moreover, nonparametric estimates made using small samples, or data which are heavily censored may be too noisy to be practical. Appropriate parametric models can make better use of available data. For inference, likelihood-based methods are well-equipped to deal with truncated and/or censored data. Furthermore, by assuming a parsimonious representation of the data-generating process, parametric models admit simpler, more intuitive ways to compare populations of interest, borrow strength across groups, and incorporate prior information.

Often no information is available to identify why a unit failed, even when the failed units are available. Physical failure mode analysis (sometimes referred to as ``autopsy'') can be extremely time consuming and expensive. This presents a dilemma for analysts: the data may indicate multiple failure modes, contraindicating the use of a unimodal parametric distribution. However, without any knowledge of cause of failure, traditional competing risk models are not identifiable. \citet{chan} proposed the Generalized Limited Failure Population (GLFP) model. This model can provide a solution to the problem of unknown cause of failure (masking) in the special case where there is evidence of two modes of failure which impact different stages of product life. It avoids non-identifiability by introducing a parameter representing the population proportion defective. Where this parameter is zero, the GLFP model reduces to a unimodal distribution. \\

@@

The structure of the paper is as follows. Section~\ref{sec:Background} introduces the proposed method and potential applications and examines previous related work in the literature.  Section~\ref{sec:GLFP model} introduces the GLFP model and illustrates its use with a subset of the Backblaze data.  In Section~\ref{sec:Data}, we describe the Backblaze Hard Drive data set, which is used throughout as a motivating example. In Section~\ref{sec:Hierarchical GLFP model} we discuss using hierarchical modeling of the GLFP model parameters to extend the GLFP model to multiple populations. Section~\ref{sec:Data analysis} applies the hierarchical GLFP model to the hard disk drive data. First, we do model selection among four models of increasing complexity, using approximate leave-one-out cross-validation. Next, for the selected model, we assess the model fit using a graphical comparison of replicated data sets generated from the posterior distribution to the observed data. Finally, we present an evaluative comparison of populations taking into account practical considerations related to product lifetime. Finally, in Section~\ref{sec:Discussion}, we suggest potential applications of our model and consider limitation for inference implied by the model assumptions.

@@

Previous papers have employed various assumptions and methods to model masked lifetime failure data.  When modeling computer system failures \citet{reiser} assumed each observed failure came from a known subset of failure modes, and estimation was performed using a Bayesian approach.  \cite{chan} labeled the cause of circuit board failures as infant mortality, unknown, or wearout based on the time of observed failures.  This helped identify parameters when using maximum likelihood (ML) estimation.  Extending Chan and Meeker's analysis, \citet{basu} performed a Bayesian analysis with informative priors to better identify early versus late failure modes without making any assumptions about the cause of failure.  \cite{berger} introduced the Poly-Weibull distribution where the failure time is the minimum of a several Weibull distributions, corresponding to different failure modes.  More recently, \cite{ranjan} considered a competing risk model for infant mortality and wearout as a mixture of Weibull and exponential failure distributions.  Treating the unknown failure modes as incomplete data, an expectation maximization (EM) algorithm providing ML estimates was used, in addition to Bayesian estimation.

@@

In order to describe the entire population, consisting of different but similar sub-populations, and because of the limited amount of data from many of the sub-populations, we model the sub-population-specific parameters hierarchically, borrowing strength across the sub-populations.  Let
\begin{equation}
y_{ig} \ind \op{GLFP}\left( \pi_g, \mu_{1g}, \sigma_{1g}, \mu_{2g}, \sigma_{2g} \right),
\end{equation}
where $g=1,\ldots,G$ indexes the sub-populations.  The likelihood for the hierarchical GLFP is a function of $\bm{\theta_g} = (\mu_{1g}, \sigma_{1g}, \mu_{2g}, \sigma_{2g}, \pi_{g})$.  Assuming the lifetimes of all units are independent within and across groups, the likelihood for the data, $i=1,\dots,n_g$,  is given by
\begin{equation*}
L(\bm{\Theta})= \prod_{g=1}^{G} \prod_{i=1}^{n_{g}} \left[\frac{f(t_{ig};\bm{\theta_g})}{1-F(t_{ig}^L;\bm{\theta_g})}\right]^{1-c_{ig}} \left[ \frac{1-F(t_{ig};\bm{\theta_g})}{1-F(t_{ig}^L;\bm{\theta_g})} \right]^{c_{ig}}
\end{equation*}
where $t_{ig}$ is the end of the observed lifetime of unit $i$ in group $g$; $t_{ig}^L$ is the left truncation time for unit $i$ in group $g$; and $c_{ig}$ is an indicator if unit $i$ in group $g$ is right censored.  All times are again in hours.

@@

As discussed in Section \ref{sec:Weibull parameterization}, we reparameterize the Weibull distribution in terms of log quantile and scale since the data we encounter are more informative about the left side of their respective lifetime distribution. We truncate the distribution of $\sigma_{2g}$ at $1$, restricting the wearout failure mode to have an increasing hazard function (e.g., $0<\sigma_{2g}<1$). We choose to model these parameters with lognormal and normal distributions because many populations require strong regularization which the normal, with its exponentially decreasing tails, provides.

@@

The set of model specifications was chosen based data, interpretation of the model, as well as estimation considerations.  Product specific parameters for the the wearout failure mode $(\mu_{2g},\sigma_{2g})$, and the proportion defective $(\pi_g)$, are considered as a means to account for heterogeneity across brands in the right tails of the failure distribution.  Going from a common model for all product brands and gradually increasing the complexity of the model, we end up at Model 4.  Model 4 allows for the probability of infant mortality as well as the shape and scale parameters for the wearout failure mode to vary by drive-model.

@@

\paragraph{Model 2.} $t_{p,g}$ varies by drive-model. To help with model identifiably, we tighten the priors on the infant mortality failure mode:
$$ \pi \sim \op{Logit-normal}\langle 7.0\times 10^{-3},\, 2.6 \times 10^{-1} \rangle,$$
$$\sigma_1 \sim \op{Log-normal}\langle 1.4 \times 10^{-1},\, 7.1\rangle,$$ 
$$t_{p1} \sim \op{Log-normal} \langle 2.2 \times 10^1,\, 5.5 \times 10^{4} \rangle.$$

@@

\subsection{Model Selection}
\label{sec:Model Comparisons}
As we have discussed, while we prefer to allow all of the GLFP model parameters to be drive-model specific, there are practical issues with fitting the full model. For example, due to heavy left-truncation, there may be insufficient information for particular drive-models to estimate all of the parameters.

Figure \ref{fig:fig2} provides a visual comparison for Models 1 through 4 by plotting the pointwise posterior median of time to failure. The large left panel shows the Kaplan-Meier nonparametric estimate of the same. The Kaplan-Meier estimates on the right side of Figure \ref{fig:fig2} shows that the set of estimated failure curves for all four models that we fit. The smaller plots correspond to Models 1 through 4.  Note that while all the paths for the posterior estimates necessarily pass through the origin, the nonparametric curves do not, but only because, for the Kaplan-Meier estimator, inference is entirely conditional on survival up to left-most left-trunctation time; to make the plot comparable, we use an adjustment based on a parametric model (Model 4).

%Should we be brief discussing the plot?
These plots suggest that Model 1 is insufficient to explain the observed data. Model 2 certainly captures more of the heterogeneity observed in the Kaplan-Meier estimates; we observe that the assumption of a common $\sigma_2(=\sigma_{2,g})$ results in a very similar progressions in the rate of failure, which may be too restrictive. Model 3, which removes this restriction on $\sigma_{2,g}$ suggests that there is evidence to support variation in this parameter among drive-models. While Model 3 and 4 do display differences, they are relatively subtle.

@@

We can also compare the four Model fits for each drive-model individually.  For these comparisons, we use the posterior median of the MCMC draws. %Unlike maximum likelihood, by including the hyperparameters in the probability model, there is a data-dependent penalization that results in shrinkage toward a common overall model.

@@

The GLFP fit for a representative selection of drive-models (Drive-models 2, 9, 14, and 40) are presented in Figure \ref{fig:mod_comp_leg} (See the Supplementary Material for similar plots for the other drive-models).  The black step functions again correspond to the adjusted Kaplan-Meier estimates.  As model complexity increases, the GLFP curves become more flexible and are better able to describe the observed failure data.  All of the GLFP models appear to produce lower estimates, relative to Kaplan-Meier, of the proportion of failed hard drives for Drive-model 2, with Model 4 being in closest agreement.  For Drive-model 14, Models 1-3 produce lower estimates of the proportion of drives failing, and for Drive-model 40, they produce higher estimates.  On the other hand, Model 4 follows the nonparametric estimate quite closely across stages of lifetime.  The differences between Models 3 and 4 and Models 1 and 2 are visually quite apparent.  Differentiating between Model 3 and 4 is less clear; for instance, the estimates from Model 3 and 4 are nearly identical for Drive-model 40.

From the point of view of a consumer of hard disk drives, the goal of an analysis such as this is may be to rate manufacturers and/or to inform future purchases based on predicted product performance. In this case, we should choose the model that will provide the most accurate prediction for future units of previously observed drive-models. One appropriate criterion for model selection, then, is the log pointwise predictive density (lpd),

@@

\noident Using this criterion, we should choose the Model with the highest expected lpd (elpd) for a new data set $\{t_{new,g,i}:g=1,\ldots,G; i=1,\ldots,n_g\}$. Suppressing the conditioning on $t^L$ and $c$,
\begin{equation}
\mbox{elpd} = \op{E}_h \mbox{lpd} = \sum_{g=1}^G \sum_{i=1}^{n_g} \int \log [p(t_{new, g, i}|t)] h(t_{new,g,i}) d t_{new,g,i},
\label{elpd}
\end{equation}
where $h$ is a density for the true distribution of $t_{new,g,i}$. Although $h$ is unknown, leave-one-out cross-validation provides a robust estimator:
\begin{equation}
\widehat{\text{elpd}} = \sum_{g=1}^G \sum_{i=1}^{n_g} \log [p(t_{g,i}|t_{-(g,i)})].
\label{loo-est}
\end{equation}
The \texttt{R} package, \texttt{loo} \citep{loo}, computes an approximation of (\ref{loo-est}) provided that the observations $t_i$ are conditionally independent. It employs an importance sampling method that uses $S$ saved MCMC draws to compute smoothed importance weights, $w_{i,s}$, approximating $\log [p(t_{g,i}|t_{-(g,i)})]$ with $\frac{\sum_{i=1}^S w_{i,s} p(t_{g,i})}{\sum_{s=1}^S w_{i,s}}$. In addition to providing an estimate of (\ref{elpd}), their method also produces a standard error based on an asymptotic result. For details, refer to \cite{vehtari}.
%When $n$ is large, the distribution of the elpd is approximately normal and different models can be compared statistically. 
% To statistically compare the GLFP Models, we estimated the predictive accuracy of the 4 different models using an approximate leave-one-out cross validation (LOO) method.  As outlined in Vehtari et. al, the predictive accuracy from a fitted Bayesian model can be estimated simply with posterior draws of the model parameters rather than re-fitting the model with different data sets \cite{vehtari}.  For each observation, $i$, the log point-wise predictive density is calculated over the full set of posterior samples with data point $i$ removed.  
% The final expected log point-wise predictive density (elpd) is the sum over all observations (elpd $=\sum{\log p(y_i|y_{-i})}$).  
Results showing estimated elpd and associated standard errors for all 4 models are shown in Table \ref{table:2}.
 We calculated the difference in expected predictive accuracy for Model 4 versus 3, Model 3 versus 2, and Model 2 versus 1, as well as the standard error of the difference (Table 1). For the models we considered, each successive increase in model complexity increases elpd.  Of all the models, Model 4 has significantly better elpd compared to the the other 3 models.

\begin{figure}
\begin{table}[H]
\centering
\begin{tabular}{rrrrrrr}
  \hline
 & $\widehat{\text{elpd}}$ \ & Difference in $\widehat{\text{elpd}}$ \ & SE of the Difference \\ 
  \hline
Model 4 & -13309.5 & 40.7 & 11.3 \\ 
Model 3 & -13350.2 & 458.8 & 31.0  \\ 
Model 2 & -13809.0 & 3674.6 & 96.2 \\ 
Model 1 & -17483.6  \\ 
   \hline
\end{tabular}
\caption{Expected Log Pointwise Predictive Density (elpd) for each model specification.  Each model is compared to the more parsimonious model below.  The estimated difference of expected leave-one-out prediction errors between the two models, as well as the standard error of the difference, is also presented.}
\label{table:2}
\end{table}
\end{figure}

\subsection{Results}
\subsubsection{Model Assessment}
\label{model-assessment}
Having chosen Model 4 as the best of the candidate models, we would like to assess whether our model provides an adequate description of the observed data. One way to do this is to draw replicate data sets from the posterior predictive distribution. This is a general approach recommended by \cite{gelman1996postpred} for models where no classical goodness-of-fit test is available. In the hierarchical setting, there can be different formulations of the predictive distribution. In the present context, one could predict the lifetime of a new unit of a previously observed drive-model or a new drive-model. We choose to focus on the former.  There are many possible approaches to the posterior predictive check. For this problem, we chose to consider the posterior predictive distribution of the Kaplan-Meier estimate for each drive-model $g$.

@@

An obstacle remains, in that the censoring mechanism itself is not fully observed. Our admittedly simple approach is to assume that failed units would have been the censored had they survived until the latest censoring or failure time for that drive model. We generated 19 replicates for each drive model. This gives a 1/20 chance under the hypothesis of no difference that the Kaplan-Meier estimate based on the observed data would be ``most extreme" relative all the replicated  from the those one and is not too many so as to produce an overly cluttered plot. Our method for generating replicate data sets, $y_{rep,g}^{(s)}$, $s = 1 \dots 19$, for each drive-model $g=1,\ldots,44$, is as follows:
\begin{enumerate}
\item Simulate $\tilde{t}_{rep,g,i}^{(s)} \sim \op{GLFP}(\pi_{g}^{(s)},\mu_1^{(s)},\sigma_1^{(s)},\mu_{2g}^{(s)}, \sigma_{2g}^{(s)})$ where each set of parameters, $\left( \pi_{g}^{(s)},\mu_1^{(s)},\sigma_1^{(s)},\mu_{2g}^{(s)}, \sigma_{2g}^{(s)} \right)$, is a random draw from the full posterior distribution.
\item Repeat step 1 until $\tilde{t}_{rep,g,i} > t_{g,i}^L$.
\item If $c_{g,i}=0$, let $c_{rep,g,i}^{(s)}=\max \{t_{g,i}: i \ge 1\}$, otherwise let $c_{rep,g,i}^{(s)}=t_{g,i}$.\\
If $\tilde{t}_{rep,g,i}^{(s)}>m_{g,i}$, set $t_{rep,g,i}^{(s)}=c_{rep,g,i}^{(s)},\; c_{rep,g,i}^{(s)}=1$, otherwise set $t_{rep,g,i}^{(s)}=\tilde{t}_{rep,g,i}^{(s)},\; c_{rep,g,i}^{(s)}=0$.
\end{enumerate}

\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-sample}
\caption{Nonparametric estimates of the proportion failing for a representative subset of drive-models. Both the original data (\textbf{bold} line) and 19 ``replicated" data sets from the posterior predictive distribution (\textit{dashed} lines) are shown.}
\label{fig:post-pred-KM}
\end{figure}

We can compare the 19 simulated data sets $y_{rep,g, i}$ to the observed data $y_{g,i}$ by using them to re-estimate the Kaplan-Meier nonparametric estimator. The resulting plots are displayed in Figure \ref{fig:post-pred-KM}. Only a representative sample of plots is shown here for brevity (see the Supplementary Material for the complete set of drive-models).  For most drive-models, the estimates based on the observed data look similar to those based on the replicated data.  There are a few drive-models, however where this is not the case. Drive-model 14 shows a discrepancy between the GFLP fit and the Kaplan-Meier fit in the right tail. In particular, the GLFP predictions appear conservative, overpredicting the proportion failing after about 2.5 years. Due to the large number of failures for this Drive-model, the posterior for the hierarchical model is similar to the stand-alone model. Other drive-models showing a lack of fit are 4 and 34. We first address Drive-model 4; our diagnosis of 34 is analogous, so the following comments extend to that Drive-model as well.

@@

We can also use the posterior draws to compute quantiles of interest, which in reliability applications is typically more informative than a measure of central tendency.  The top panel of Figure 9 shows $t_{0.10}$ (i.e., the amount of time it takes for 10\% of hard drives to fail), for all drive-models.  In this application 50\% CIs are more meaningful as there is lots of uncertainty in some of the parameters: especially for those with few drives in operation.  The best six drive-models ranked by MTTF are also the drive-models with the largest $t_{0.10}$.  Another interesting feature to compare is $\pi$, the proportion defective.  The bottom panel of Figure 10 shows the posterior credible intervals of $\pi$ for each drive-model.  The plot is again sorted according to $t_{0.10}$ so it can be compared to the plot above.  While for many of the drive-models the ordinal ranking is the same as on the top, there are some drive-model comparisons, for example 23 and 18, that differ in ranking if compared using $t_{0.10}$ or $\pi$.  Depending on a user's application or the hard drive warranty length, using the $\pi$'s as a comparison tool may be a relevant parameter of interest.
